Notes on Validated Model Counting \\ Version of \today

### 2022-08-06 doc/mc-notes.tex
Update terminology

>>>>

POGs are inspired by the DDNNF graphs devised by
Darwiche for encoding Boolean functions, a process he refers to as
``knowledge compilation.''
POGs generalize DDNNF in two ways:
\begin{itemize}
\item It allows negation of arbitrary nodes in the graph, not just
  variables.  It is therefore not a negation-normal form.  We will see
  examples where this allows a more compact representation.
\item It allows arbitrary arguments to a $\por$ operation, as long as
  they have disjoint satisfying assignments.  By contrast, for each
  disjunction node in a DDNNF, there must be a variable $x$ such that
  the assignments for one argument have $x=1$ while those for
  the other argument to have $x=0$.
\end{itemize}
  Both of these generalizations allow more flexibility in the POG
  representation while maintaining the ability to easily compute their
  cost for separable cost functions.
